---
title: "Exploring plotly"
author: "J. Allen Baron"
date: "June 16, 2018"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
---

# Nice Plotly Features
I made notes outlining the useful features of plotly [here](https://docs.google.com/document/d/18X_NBS_dIlHVfX4MxPYNCg2iuiNRt9pnS417XLGHXso/edit?usp=sharing).

From that list I think some worth exploring include:

1. Subplots
2. Custom hover info
3. Custom controls (buttons, dropdowns, sliders, etc.)

I'm going to combine these to create a cool visualization (hopefully without too much effort).

# The Topic
I want to use something non-controversial that people generally just tend to find interesting. I was initially thinking savings vs expenditures by state or country as a picture of household financial health but access to the data is not as straightforward as I'd expected and economics are so overdone. So, I'll go with **baby names in the US**.

# The Plan
I'll create 2 plots as follows:

1. Choropleth map applying to most recent year of data
    - _Color_ = overall US ranking of #1 name in state
        - **Question answered:** Where does each state's most popular name fall among all US names? Should allow us to determine which states prefer less popular names.
        - **Hypothesis:** The most popular name in the US will most likely also be the most popular in states with the largest number of births (I hadn't planned to calculate this but I might).
    - _Custom hover info_ = Most popular baby name in state, overall US ranking, and number of states where this name is most popular
    - _Button_ = (optional) toggle boy/girl names
2. Line graph of top 10 baby names over time
    - _y-axis_ = ranking
    - _x-axis_ = year
    - _Range slider_ = change time (to zoom in on period of interest)
    - _Custom hover info_ = name, rank (x-axis), year (y-axis)
        - other info? ... maybe all-time popularity (over all years), number of years at #1
    - NOTE: I'm going to have to keep an eye on the legend to make sure it doesn't get too large... and fitting this with the chloropleth might be a bit tricky. Some adjustments will need to be made probably.

# Get the Data
Thank you [US Social Security Administration](https://www.ssa.gov/OACT/babynames/limits.html)! The data comes zipped as .txt files by year (for National data) or by state, with 1 file per year or state respectively. I'm going to have to combine this data into 2 dataframes (instead of a ton of files). The data in files are separated by commas. 

```{r libraries, include = FALSE}
library(tidyverse)
library(plotly)
library(lubridate)
library(RColorBrewer)
library(hues)
```

```{r download, eval = FALSE}
download.file("https://www.ssa.gov/OACT/babynames/names.zip",
              destfile = "./plotly_data/names.zip") # national data
download.file("https://www.ssa.gov/OACT/babynames/state/namesbystate.zip",
              destfile = "./plotly_data/namesbystate.zip") # state data

# time of download
Sys.time() %>%
    format(., format = "%e %b %Y at %H:%M:%S", usetz = TRUE) %>%
    saveRDS(., file = "./plotly_data/dl_timestamp.Rdata")
```

```{r load_data, results = 'hide', message = FALSE}
# unzip files to tempdir & list
td <- tempdir()
unzip("./plotly_data/names.zip", exdir = td)
unzip("./plotly_data/namesbystate.zip", exdir = td)
US_txt <- list.files(td, "^yob.*\\.txt$", full.names = TRUE)
state_txt <- list.files(td, "^[A-Z]{2}\\.TXT$", full.names = TRUE)

# combine into 2 dataframes
US_baby <- map(US_txt,
               ~ read_csv(.x,
                         col_names = c("Name", "Sex", "n"),
                         col_types = "cci"
                         ) %>%
                   mutate(., Year = as.integer(str_extract(.x, "[0-9]{4}"))) # add year
               ) %>%
           reduce(rbind)

state_baby <- map(state_txt,
               ~ read_csv(.x,
                         col_names = c("State", "Sex", "Year", "Name", "n"),
                         col_types = "ccici"
                         )
               ) %>%
           reduce(rbind)
```

# Create the plots

## Calculations

```{r US_wrangling}
US_no1 <- US_baby %>%
    group_by(., Sex, Year) %>%
    filter(., n == max(n)) %>%
    add_count(., Name)
US_no1

yrs_no1 <- ungroup(US_no1) %>%
    count(., Name, Sex, sort = TRUE)
yrs_no1

US_2017 <- filter(US_baby, Year == 2017) %>%
    arrange(., desc(n)) %>%
    mutate(., US_rank = row_number())

US_2017
```

```{r state_wrangling}
state_last <- filter(state_baby, Year == max(Year)) %>%
    group_by(., State, Sex) %>%
    filter(., n == max(n)) %>%
    add_count(., sort = TRUE) %>%
    left_join(., select(US_2017, Name, Sex, US_rank), by = c("Name", "Sex"))

state_no1 <- ungroup(state_last) %>%
    count(., Name, Sex) %>%
    rename(., num_states = nnn)
state_no1

state_comb <- left_join(state_last, state_no1, by = c("Name", "Sex")) %>%
    mutate(., # combine info for ties
       Name2 = if_else(
           lead(paste(State, Sex, Year, n), 1) == paste(State, Sex, Year, n),
           paste(Name, lead(Name, 1), sep = " / "),
           NA_character_,
           missing = Name
           ),
       US_rank2 = if_else(
           lead(paste(State, Sex, Year, n), 1) == paste(State, Sex, Year, n),
           paste(US_rank, lead(US_rank, 1), sep = " / "),
           NA_character_,
           missing = as.character(US_rank)
           ),
       num_states2 = if_else(
           paste(State, Sex, Year, n) == lead(paste(State, Sex, Year, n), 1),
           paste(num_states, lead(num_states, 1), sep = " / "),
           NA_character_,
           missing = as.character(num_states)
           )
     )

# remove second line for ties, add hover text
state_final <- filter(state_comb, nn == 1 | (nn == 2 & grepl("/", Name2))) %>%
    mutate(.,
           hover = paste(
               if_else(nn > 1, "TIE - ", ""), Name2,
               "<br>Total births = ", n,
               "<br>US rank = ", US_rank2,
               "<br>No. of states where #1 = ", num_states2,
               sep = ""
               )
    )
state_final <- ungroup(state_final) %>%
    mutate(., Sex = recode(Sex, "M" = "Boy", "F" = "Girl")) %>%
    left_join(., as_tibble(cbind(state.abb, state.name)), by = c("State" = "state.abb"))

state_final
```

## Create the choropleth

Got the transform and button info from:
https://community.plot.ly/t/need-help-on-using-dropdown-to-filter/6596/2

Color info from:
https://moderndata.plot.ly/create-colorful-graphs-in-r-with-rcolorbrewer-and-plotly/

This choropleth works and the button changes the data like I want but I can't figure out how to get the data change _AND_ the color change.
```{r}
# specify some map projection/options
ch_opts <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = FALSE
)

p <- plot_geo(state_final, locationmode = 'USA-states') %>%
    add_trace(., type = "choropleth",
        z = ~US_rank, text = ~hover, locations = ~State,
        color = ~US_rank, colors = "PuRd", 
        transforms = list(
            list(
                type = "filter",
                target = ~Sex,
                operation = "=",
                value = c("Boy", "Girl"),
                z = ~US_rank
            )
        )
        ) %>%
    colorbar(title = "U.S. Rank") %>%
    layout(
        title = '2017 Most Popular Baby Names in US by State<br>(Hover for breakdown)',
        geo = ch_opts,
        updatemenus = list(
            list(
                type = 'buttons',
                active = 0,
                buttons = list(
                    list(method = "restyle",
                         args = list("transforms[0].value", "Boy"),
                         label = "Boy"),
                    list(method = "restyle",
                         args = list("transforms[0].value", "Girl"),
                         label = "Girl")
                )
            )
        )
    )


p
```

### Ask SO
The documentation on plotly for R is just too poor. There are a handful of examples on how to enter something but none of the explanation about why a certain approach is used (and multiple instances in the documentation that say "all the options follow below" without any options.

Time to ask the Stack Overflow community. Creating a minimal, reproducible example.
```{r SO_minimal, eval = FALSE}
# prep data for SO
df <- select(state_final, code = State, sex = Sex, us_rank = US_rank) %>%
    mutate(., sex = recode(sex, "Boy" = "M", "Girl" = "F"))

dput(df)

# put everything below this on SO
    df <- structure(list(code = c("AK", "WI", "WY", "AK", "AL", "AL", "AR", 
    "AR", "AZ", "AZ", "CA", "CA", "CO", "CO", "CT", "CT", "DC", "DC", 
    "DE", "DE", "FL", "FL", "GA", "GA", "HI", "HI", "IA", "IA", "ID", 
    "ID", "IL", "IL", "IN", "IN", "KS", "KS", "KY", "KY", "LA", "LA", 
    "MA", "MA", "MD", "MD", "ME", "ME", "MI", "MI", "MN", "MN", "MO", 
    "MO", "MS", "MS", "MT", "MT", "NC", "NC", "ND", "ND", "NE", "NE", 
    "NH", "NH", "NJ", "NJ", "NM", "NM", "NV", "NV", "NY", "NY", "OH", 
    "OH", "OK", "OK", "OR", "OR", "PA", "PA", "RI", "RI", "SC", "SC", 
    "SD", "SD", "TN", "TN", "TX", "TX", "UT", "UT", "VA", "VA", "VT", 
    "VT", "WA", "WA", "WI", "WV", "WV", "WY"), sex = c("F", "F", 
    "M", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", 
    "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", 
    "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", 
    "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", 
    "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", 
    "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", 
    "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", "M", "F", 
    "M", "F", "M", "F", "M", "M", "F", "M", "F"), us_rank = c(1L, 
    1L, 2L, 9L, 5L, 7L, 1L, 14L, 1L, 2L, 1L, 4L, 1L, 2L, 3L, 4L, 
    5L, 9L, 3L, 10L, 6L, 2L, 5L, 7L, 1L, 2L, 28L, 15L, 1L, 15L, 3L, 
    4L, 1L, 15L, 1L, 15L, 1L, 7L, 3L, 2L, 1L, 11L, 5L, 2L, 18L, 15L, 
    1L, 2L, 3L, 15L, 3L, 7L, 5L, 7L, 3L, 9L, 5L, 7L, 1L, 15L, 1L, 
    15L, 18L, 10L, 1L, 2L, 13L, 4L, 1L, 2L, 3L, 2L, 1L, 2L, 1L, 7L, 
    1L, 15L, 1L, 2L, 18L, 17L, 5L, 7L, 1L, 15L, 5L, 7L, 1L, 4L, 3L, 
    15L, 3L, 2L, 26L, 37L, 3L, 2L, 29L, 1L, 2L, 1L)), class = c("tbl_df", 
    "tbl", "data.frame"), row.names = c(NA, -102L))

    library(magrittr)
    library(plotly)
    
    geo_opts <- list(
      scope = 'usa',
      projection = list(type = 'albers usa'),
      showlakes = FALSE
    )

    plot_geo(df, locationmode = 'USA-states') %>%
        add_trace(., type = "choropleth",
            z = ~us_rank, locations = ~code, color = ~us_rank, 
            transforms = list(
                list(
                    type = "filter",
                    target = ~sex,
                    operation = "=",
                    value = c("M", "F")
                )
            )
            ) %>%
        layout(
            geo = geo_opts,
            updatemenus = list(
                list(
                    type = 'buttons',
                    active = 0,
                    buttons = list(
                        list(method = "restyle",
                             args = list("transforms[0].value", "M"),
                             label = "Boy"),
                        list(method = "restyle",
                             args = list("transforms[0].value", "F"),
                             label = "Girl")
                    )
                )
            )
        )

```

### Choropleths side-by-side

Notes about `Layout()`:

- Needs to be called with each choropleth to provide geo options
- Title can only be specified for entire plot (if multiple, value will be last `title =` call in `layout()`
- How to control subplot margins = **unknown**; call in individual plot layout has no effect
- Cannot move 2nd colorbar/legend ('boys' map)
- Annotations seem to work better when called in `layout()` after calling `subplot()`
```{r}
boy <- filter(state_final, Sex == "Boy")
girl <- filter(state_final, Sex == "Girl")

# specify some map projection/options
ch_opts <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = FALSE
)

boy_ch <- plot_geo(boy, locationmode = 'USA-states') %>%
    add_trace(., type = "choropleth",
        z = ~US_rank, text = ~hover, locations = ~State,
        zauto = FALSE, zmin = 1, zmax = 30,
        color = ~US_rank, colors = "GnBu", reversescale = TRUE
        ) %>%
    colorbar(title = "U.S. Rank", y = -1) %>%
    layout(., geo = ch_opts)


girl_ch <- plot_geo(girl, locationmode = 'USA-states') %>%
    add_trace(., type = "choropleth",
        z = ~US_rank, text = ~hover, locations = ~State,
        zauto = FALSE, zmin = 1, zmax = 30,
        color = ~US_rank, colors = "PuRd", reversescale = TRUE
        ) %>%
    colorbar(., title = "U.S. Rank", x = 0.45) %>%
    layout(., geo = ch_opts)

subplot(girl_ch, boy_ch) %>%
    layout(annotations = list(
        list(
            text = "2017 Girl Names",
            xref = "paper", xanchor = "center", x = 0.25,
            yref = "paper", yanchor = "bottom", y = 0.1,
            align = "center",
            showarrow = FALSE
            ),
        list(
            text = "2017 Boy Names",
            xref = "paper", xanchor = "center", x = 0.75,
            yref = "paper", yanchor = "bottom", y = 0.1,
            align = "center",
            showarrow = FALSE
            )
        )
    )
```
I'm going to leave this where it is for now. It's definitely not what I was hoping for but the documentation is rough.

# Top 5 names by year
```{r US_rank_yrs}
top5 <- group_by(US_baby, Sex, Year) %>%
    top_n(., n = 5, wt = n) %>%
    arrange(., desc(n)) %>%
    mutate(., rank = row_number())

top5_50y <- ungroup(top5) %>%
    filter(., Year >= (max(Year) - 50)) %>%
    mutate(., Sex = recode(Sex, "M" = "Boy", "F" = "Girl"))
arrange(top5_50y, Year, Sex)
unique(top5_50y$Year) %>% sort()

girl5 <- filter(top5_50y, Sex == "Girl")
boy5 <- filter(top5_50y, Sex == "Boy")

girl_n <- n_distinct(girl5$Name)
boy_n <- n_distinct(boy5$Name)

col_palette <- colorRampPalette(brewer.pal(9, "Set1"))

n_distinct(top5$Name) # count total unique names (need a color palette with enough colors)

girl_g <- ggplot(data = girl5, aes(x = Year, y = rank)) +
    geom_line(aes(color = Name)) +
    scale_y_reverse()

boy_g <- ggplot(data = boy5, aes(x = Year, y = rank)) +
    geom_line(aes(color = Name)) +
    scale_y_reverse()

col_palette <- colorRampPalette(brewer.pal(9, "Set1"))

subplot(girl_g, boy_g)

# boy/girl split by facet (too many names)
ggplot(data = top5, aes(x = Year, y = rank)) +
    geom_point(aes(color = Name)) +
    facet_grid(Sex ~ .)

plot_ly(data = top5, x = ~Year, y = ~rank,
        color = ~Name,
        type = "scatter", mode = "lines")

# doesn't work with transforms...
us_p <- plot_ly(data = top5, x = ~Year, y = ~rank,
        color = ~Name, colors = col_palette(n_distinct(top5_50y$Name)),
        type = "scatter", mode = "lines",
        transforms = list(
            list(
                type = 'filter',
                target = 'Sex',
                operation = '=',
                value = c("Boy", "Girl")
                )
            )
  )

us_p %>%
    layout(.,
           updatemenus = list(
               list(
                type = 'buttons',
                active = 0,
                buttons = list(
                    list(method = "restyle",
                         args = list("transforms[0].value", "Boy"),
                         label = "Boy"),
                    list(method = "restyle",
                         args = list("transforms[0].value", "Girl"),
                         label = "Girl")
                    )
                )
           )
    )


```

Make lines appear by using simpler case (works!)
```{r}
col_palette <- colorRampPalette(brewer.pal(9, "PuRd")[5:9])

# testing out package `hues` (clustering to get n distinct colors)
library(hues)

col_palette(girl_n)
iwanthue(girl_n) %>% attributes()

# girls plot
arrange(girl5, Year) %>%
plot_ly(data = ., type = 'scatter', mode = 'lines+markers',
        x = ~Year, y = ~rank, color = ~Name, colors = unname(iwanthue(girl_n))
) %>%
    layout(.,
           yaxis = list(
               tickmode = 'linear', tick0 = 1, dtick = 1,
               autorange = "reversed",
               title = "Rank"
               ),
           xaxis = list(
               title = "Year"
           )
        )

# boys plot
arrange(boy5, Year) %>%
plot_ly(data = ., type = 'scatter', mode = 'lines+markers', connectgaps = FALSE,
        x = ~Year, y = ~rank, color = ~Name, colors = unname(iwanthue(boy_n))
) %>%
    layout(.,
           yaxis = list(
               tickmode = 'linear', tick0 = 1, dtick = 1,
               autorange = "reversed",
               title = "Rank"
               ),
           xaxis = list(
               title = "Year"
           )
        )

# just discovered that lines connect without gaps --> need NA values to create gaps
#   in plotly
```

How do I add the missing years with NA values in rank? (This is something I should be able to do)
```{r}
girl5
filter(girl5, Name == "Abigail")

# years 1967 - 2017
t <- spread(girl5, key = Name, value = rank) %>%
    gather(., key = "Name", value = "rank", -Sex, -n, -Year, na.rm = FALSE)
t
count(t, Name)
```

This makes `n` incorrect. A better way to do this might be to go back to the original data, identify the top 5 names each year, filter every name, then either:

1. create rank for the top 5 only (and leave NA everywhere else)
2. ranke each name for every year and replace anything less than 5 with NA (or leave the rank)

```{r top5_allRank}
tmp_50yr <- mutate(US_baby, Sex = recode(Sex, "F" = "Girl", "M" = "Boy")) %>%
    filter(., Year >= max(Year) - 50) %>%
    group_by(., Sex, Year) %>%
    arrange(., desc(n)) %>%
    mutate(., Rank = row_number())

top_girls <- filter(tmp_50yr, Rank <= 5 & Sex == "Girl") %>%
    {unique(.$Name)} # some unfortunate girls were given boy names => filter by sex too

top_boys <- filter(tmp_50yr, Rank <= 5 & Sex == "Boy") %>%
    {unique(.$Name)} # some unfortunate girls were given boy names => filter by sex too


girl5 <- filter(tmp_50yr, Name %in% top_girls & Sex == "Girl") %>%
    arrange(., Name, Year)
boy5 <- filter(tmp_50yr, Name %in% top_boys & Sex == "Boy") %>%
    arrange(., Year)
```

```{r}
girl_n <- n_distinct(girl5$Name)
boy_n <- n_distinct(boy5$Name)

plot_ly(data = girl5, type = 'scatter', mode = 'lines+markers',
        x = ~Year, y = ~Rank, color = ~Name, colors = unname(iwanthue(girl_n))
        ) %>%
    layout(., yaxis = list(autorange = "reversed"))

filter(girl5, Name == "Madison") 
```

Well, that worked but I had assumed that the top 5 names for any given year would always be in the top 1000 and therefore have a rank for each year. That is not the case for all names (example: Madison).

Well, I could go back to the spread/gather approach and before spreading paste `n` and `Rank` together so they are spread correctly and then split them after gathering. I could afterward replace `NA` values in `Rank` with `>1000` but I don't think I'll do that. I think I'll just leave it `NA`.

```{r}
glimpse(girl5)
girl5_2 <- unite(girl5, col = n_Rank, n, Rank, sep = "_") %>%
    spread(., key = Year, value = n_Rank) %>%
    gather(., key = "Year", value = "n_Rank", -Name, -Sex, na.rm = FALSE) %>%
    separate(., col = n_Rank, into = c("n", "Rank"), sep = "_", remove = TRUE, convert = TRUE)

plot_ly(data = girl5_2, type = 'scatter', mode = 'lines+markers',
        x = ~Year, y = ~Rank, color = ~Name, colors = unname(iwanthue(girl_n))
        ) %>%
    layout(., yaxis = list(autorange = "reversed"))
```


Just too busy, will scale down to the top 2 names each year

```{r top2_allRank}
top2_50yr <- mutate(US_baby, Sex = recode(Sex, "F" = "Girl", "M" = "Boy")) %>%
    filter(., Year >= max(Year) - 50) %>%
    group_by(., Sex, Year) %>%
    arrange(., desc(n)) %>%
    mutate(., Rank = min_rank(-n))

top2_girls <- filter(top2_50yr, Rank <= 2 & Sex == "Girl") %>%
    {unique(.$Name)} # some unfortunate girls were given boy names => filter by sex too

girl2 <- filter(top2_50yr, Name %in% top2_girls & Sex == "Girl") %>%
    arrange(., Name, Year) %>%
    unite(., col = n_Rank, n, Rank, sep = "_") %>%
    spread(., key = Year, value = n_Rank) %>%
    gather(., key = "Year", value = "n_Rank", -Name, -Sex, na.rm = FALSE) %>%
    separate(., col = n_Rank, into = c("n", "Rank"), sep = "_",
             remove = TRUE, convert = TRUE)

top2_boys <- filter(top2_50yr, Rank <= 2 & Sex == "Boy") %>%
    {unique(.$Name)} # some unfortunate girls were given boy names => filter by sex too

boy2 <- filter(top2_50yr, Name %in% top2_boys & Sex == "Boy") %>%
    arrange(., Year) %>%
    unite(., col = n_Rank, n, Rank, sep = "_") %>%
    spread(., key = Year, value = n_Rank) %>%
    gather(., key = "Year", value = "n_Rank", -Name, -Sex, na.rm = FALSE) %>%
    separate(., col = n_Rank, into = c("n", "Rank"), sep = "_",
             remove = TRUE, convert = TRUE)
```

```{r}
plot_ly(data = girl2, type = 'scatter', mode = 'lines+markers',
        x = ~Year, y = ~Rank, color = ~Name, colors = unname(iwanthue(girl_n))
        ) %>%
    layout(., yaxis = list(range = c(5.5, 0.5)))
```

These should match if the calculations were right... some values are being dropped. WHY?
```{r}
filter(US_baby, Name == "Madison", Year == 1977)
filter(girl2, Name == "Madison", Year == 1977)
```
I thought it was because input was `tmp_50yr` instead of `top2_50yr` but that did not fix the problem. Examine each dataframe to see when data is dropped

```{r}
filter(US_baby, Name == "Madison", Year == 1977) # this is taking into account boys names
filter(top2_50yr, Name == "Madison", Year == 1977) # still here
filter(girl2, Name == "Madison", Year == 1977) # missing
```

So, it's lost in the creation of `girl2`. Where? Is `top2_girls` correct?

```{r}
filter(top2_50yr, Sex == "Girl", Rank <= 2) %>%
    arrange(., Year, Rank) %>%
    .$Name %in% top2_girls %>%
    all()
```

Appears to be. Now for `girl2`.

```{r}

# is each name-sex combination present for 1967-2017 in top2_50yr?
all_yrs <- unique(top2_50yr$Year) %>%
        sort(.)
girl2 <- filter(top2_50yr, Name %in% top2_girls & Sex == "Girl")
group_by(girl2, Name) %>%
    summarize(., sum(Year %in% all_yrs, na.rm = TRUE))
```

Apparently only 'Madison' is missing. Why? Is it present in the original data?

```{r}
filter(US_baby, Name == "Madison" & Sex == "F") %>%
    arrange(., Year)
```

Nope. Okay, so there are NO ERRORS... that's just the way the data is. I guess 'Madison' was a very unpopular name for girls before 1984 and didn't really even exist before 1970. Just out of curiosity... what about boys named 'Madison'? and compared to girls?

```{r}
madison <- filter(US_baby, Name == 'Madison') %>%
        arrange(., Year)

# boys name popularity
filter(madison, Sex == 'M') %>%
    ggplot(., aes(x = Year, y = n)) +
        geom_line()

# boys vs girls popularity
ggplot(madison, aes(x = Year, y = n, color = Sex)) +
    geom_line()
```
Similar trend but the name never really caught on for boys... probably because people overwhelmingly preferred it for girls.

# ioslides formatting efforts

## CSS didn't reduce font size
<style>
div.code {
    font-size: 50%;
}

div.smallnote {
    font-size: 75%;
}
</style>

## sessionInfo {.smaller}
<div class = "code">
```{r, echo = FALSE}
sessionInfo()
```
</div>
