---
title: "Exploring plot_ly for creating maps"
author: "J. Allen Baron"
date: "May 22, 2018"
output: html_notebook
---

```{r libraries, include = FALSE}
library(tidyverse)
library(RSocrata)
library(sf)
library(plotly)
```

## Prepare Data (copied from JABaron_leaflet.Rmd)
### Load Baltimore vacant (_i.e._ boarded up) houses data
```{r load_data, results = 'hide'}
balt_vacant <- read.socrata("https://data.baltimorecity.gov/resource/rw5h-nvv4.csv")
```

### Tidy location data
```{r, tidy_location, message = FALSE}
location <- str_split(balt_vacant$location, pattern = " ", simplify = TRUE) %>%
    as_tibble()
colnames(location) <- c("location_type", "longitude", "latitude")

location <- purrr::map_dfc(location,
                      ~ str_remove_all(.x, pattern = "\\(|\\)") %>%
                          str_trim(.)
                      ) %>%
            type_convert(.)

balt_vacant <- cbind(balt_vacant, location)

lon_range <- range(balt_vacant$longitude)
lat_range <- range(balt_vacant$latitude)
```

### Load Baltimore neighborhood boundaries
To give someone not familiar with Baltimore some context
```{r neighborhood_data}
neighborhoods <- read_sf("https://data.baltimorecity.gov/resource/h3fx-54q3.geojson")
nb <- st_read("https://data.baltimorecity.gov/resource/h3fx-54q3.geojson")
```

```{r nb_latlong}
nb <- neighborhoods$geometry[[1]] %>%
    as.matrix() %>%
    as_tibble() %>%
    rename(longitude = V1, latitude = V2)
```

# Try out plotly
```{r plotly_vacants}
plot_ly() %>%
    add_trace(data = balt_vacant, type = 'scattergeo', mode = 'markers',
                lon = ~longitude, lat = ~latitude
                ) %>%
    add_trace(data = neighborhoods, type = 'scattergeo', mode = 'lines') %>%
    layout(geo = list(scope = 'USA'))


plot_geo() %>%
    add_trace(data = balt_vacant, type = 'scattergeo', mode = 'markers',
                lon = ~longitude, lat = ~latitude
                ) %>%
        # this doesn't draw neighborhood lines for some reason (object type?)
    add_polygons(data = nb, x = ~longitude, y = ~latitude) %>%
    layout(geo = list(
        scope = 'usa',
        lonaxis = list(range = lon_range),
        lataxis = list(range = lat_range)
        )
        )

plot_ly(neighborhoods)
class(neighborhoods)
class(nb)
View(nb)
as.matrix(neighborhoods$geometry)
t <- neighborhoods$geometry[[1]]
str(t)
```


```{r}
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2011_february_us_airport_traffic.csv')

# geo styling
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB("gray95"),
  subunitcolor = toRGB("gray85"),
  countrycolor = toRGB("gray85"),
  countrywidth = 0.5,
  subunitwidth = 0.5
)

p <- plot_geo(df, lat = ~lat, lon = ~long) %>%
  add_markers(
    text = ~paste(airport, city, state, paste("Arrivals:", cnt), sep = "<br />"),
    color = ~cnt, symbol = I("square"), size = I(8), hoverinfo = "text"
  ) %>%
  colorbar(title = "Incoming flights<br />February 2011") %>%
  layout(
    title = 'Most trafficked US airports<br />(Hover for airport)', geo = g
  )
p
head(df)
```

```{r direct_copy}
#### DON'T WORK!!! ####
# from https://moderndata.plot.ly/visualizing-geo-spatial-data-with-sf-and-plotly/
plot_ly(franconia, split = ~NAME_ASCI)

plot_ly(
  franconia, 
  split = ~NUTS_ID,
  color = ~SHAPE_AREA,
  alpha = 1,
  showlegend = FALSE
)
```

```{r altered}
# from https://moderndata.plot.ly/visualizing-geo-spatial-data-with-sf-and-plotly/
plot_ly(franconia, split = ~NAME_ASCI, type = 'scattergeo', mode = 'lines',
        linetype = 'solid')
%>%
    layout(geo = list(
        scope = 'usa',
        lonaxis = list(range = lon_range),
        lataxis = list(range = lat_range)
        )
        )

plot_ly(
  franconia, 
  split = ~NUTS_ID,
  color = ~SHAPE_AREA,
  alpha = 1,
  showlegend = FALSE
)
```

# CONCLUSION
I don't really like plotly for maps. Maybe combining it with something else would make it better but it isn't very intuitive and needs a lot of tweaking to make it work.