---
title: "U.S. Baby Name<br>Popularity, 1967-2017"
subtitle: "Presentation with Plotly<br>Developing Data Products - Week 3"
author: "J. Allen Baron"
date: "July 2, 2018"
output:
    ioslides_presentation:
        smaller: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include = FALSE}
library(tidyverse)
library(plotly)
library(hues)
```

## Goal

#### To explore the popularity of girls and boys baby names in the U.S. over the last 50 years (1967-2017).

<br><br>

#### NOTES:

1. To reduce complexity, only those names which reached #1 or #2 in _at least one year_ are included.

```{r download, include = FALSE, eval = FALSE}
### Download 
download.file("https://www.ssa.gov/OACT/babynames/names.zip",
              destfile = "./plotly_data/names.zip") # national data

# time of download
Sys.time() %>%
    format(., format = "%e %b %Y at %H:%M:%S", usetz = TRUE) %>%
    saveRDS(., file = "./plotly_data/dl_timestamp.Rdata")
```
  

2. Data was downloaded from the [U.S. Social Security Administration](https://www.ssa.gov/OACT/babynames/) on `r readRDS(file = "./plotly_data/dl_timestamp.Rdata")`.
3. For the code, examine the original .Rmd file.

```{r load_data, include = FALSE}
### Load into R
# unzip files to tempdir & list
td <- tempdir()
unzip("./plotly_data/names.zip", exdir = td)

US_txt <- list.files(td, "^yob.*\\.txt$", full.names = TRUE)

# combine into 2 dataframes
US_baby <- map(US_txt,
               ~ read_csv(.x,
                         col_names = c("Name", "Sex", "n"),
                         col_types = "cci"
                         ) %>%
                   mutate(., Year = as.integer(str_extract(.x, "[0-9]{4}"))) # add year
               ) %>%
           reduce(rbind)
```

```{r top2_allRank, include = FALSE}
## Filter data by Top 2 names each year
# establish rank by year for girls and boys
last50 <- mutate(US_baby, Sex = recode(Sex, "F" = "Girl", "M" = "Boy")) %>%
    filter(., Year >= max(Year) - 50) %>%
    group_by(., Sex, Year) %>%
    arrange(., desc(n)) %>%
    mutate(., Rank = min_rank(-n))

# identify top 2 girls' names for each year
top2_girls <- filter(last50, Rank <= 2 & Sex == "Girl") %>%
    {unique(.$Name)} # some unfortunate girls were given boy names => filter by sex too

# get data for all years for any girl's name that reached the top 2 at least once
girls <- filter(last50, Name %in% top2_girls & Sex == "Girl") %>%
    arrange(., Name, Year) %>%
    # Represent years with no data for a name with 'NA' to make lack of name
    #   popularity evident (i.e. < 5 girls with that name that year)
    unite(., col = n_Rank, n, Rank, sep = "_") %>%
    spread(., key = Year, value = n_Rank) %>%
    gather(., key = "Year", value = "n_Rank", -Name, -Sex, na.rm = FALSE) %>%
    separate(., col = n_Rank, into = c("n", "Rank"), sep = "_",
             remove = TRUE, convert = TRUE)

# same for boys
top2_boys <- filter(last50, Rank <= 2 & Sex == "Boy") %>%
    {unique(.$Name)}

boys <- filter(last50, Name %in% top2_boys & Sex == "Boy") %>%
    arrange(., Year) %>%
    unite(., col = n_Rank, n, Rank, sep = "_") %>%
    spread(., key = Year, value = n_Rank) %>%
    gather(., key = "Year", value = "n_Rank", -Name, -Sex, na.rm = FALSE) %>%
    separate(., col = n_Rank, into = c("n", "Rank"), sep = "_",
             remove = TRUE, convert = TRUE)
```

## Popularity of Girls' Names
```{r, echo = FALSE}
girl_colors <- top2_girls %>%
    length(.) %>%
    iwanthue(.) %>%
    unname(.)

plot_ly(data = girls, type = 'scatter', mode = 'lines+markers',
        x = ~Year, y = ~Rank, color = ~Name, colors = girl_colors
        ) %>%
    layout(., yaxis = list(range = c(25.5, 0.5)))
```
  
- NOTE: Only those girls' names that reached the Top 2 in at least one year are included.

## Popularity of Boys' Names
```{r, echo = FALSE}
boy_colors <- top2_boys %>%
    length(.) %>%
    iwanthue(.) %>%
    unname(.)

plot_ly(data = boys, type = 'scatter', mode = 'lines+markers',
        x = ~Year, y = ~Rank, color = ~Name, colors = boy_colors
        ) %>%
    layout(., yaxis = list(range = c(25.5, 0.5)))
```
  
- NOTE: Only those boys' names that reached the Top 2 in at least one year are included.